A Possibilistic Valid-time Model

### 2012-04-05 trunk/ipmu2012/proposal.tex
modifications to fit 10 pages

%\subsubsection{The database}
\paragraph{The database}
Consider the example relation given in Table \ref{tb:car-models} describing car models, containing general attributes (model name, manufacturer, car segment) and one temporal attribute (stored as explained in subsection \ref{subsec:storage}) describing the approximate period of time during which the car model was sold. The value for $D$ is stored in \emph{yyyy} format and $a$ and $b$ are represented by an integer. The ID field identifies a car model while the field Instance ID (IID) identifies the instance for a car model, thus a car model in a certain state.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Sample table for the car models. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
\centering
\caption{Example database}
\begin{tabular}{c c c c c c c}
\hline
ID & IID & Segment & Manufacturer & Name & Start & End  \\ [0.5ex]
\hline
001 & 1 & B & Peugeot & 205 & [1985,2,3] & [1997,2,1] \\
002 & 1 & C & Peugeot & 305 & [1977,2,2] & [1989,2,3] \\
003 & 1 & B & Citroen & C2 & [2002,2,2] & [2006,1,1] \\
001 & 2 & B & Peugeot & 206 & [2000,1,2] & [2011,2,1] \\
001 & 3 & B & Peugeot & 207 & [2006,1,1] & [2011,1,1]\\
\hline
\end{tabular}
\vspace{10pt}

\label{tb:car-models}

\vspace{-30pt}

%\subsubsection{The query}
%\paragraph{The database}
Consider the following query:
\begin{center}
\emph{The user wants to obtain a list of models from segment B, made by manufacturer Peugeot before the year interval 2001-2005}
\end{center}

@@

\end{example}

>>>>

%\subsubsection{The database}
%\paragraph{The database}
Consider the example relation given in Table \ref{tb:car-models} describing car models, containing general attributes (model name, manufacturer, car segment) and one temporal attribute (stored as explained in subsection \ref{subsec:storage}) describing the approximate period of time during which the car model was sold. The value for $D$ is stored in \emph{yyyy} format and $a$ and $b$ are represented by an integer. The ID field identifies a car model while the field Instance ID (IID) identifies the instance for a car model, thus a car model in a certain state.

\end{example}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Sample table for the car models. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
\centering
\caption{Example database}
\begin{tabular}{c c c c c c c}
\hline
ID & IID & Segment & Manufacturer & Name & Start & End  \\ [0.5ex]
\hline
001 & 1 & B & Peugeot & 205 & [1985,2,3] & [1997,2,1] \\
002 & 1 & C & Peugeot & 305 & [1977,2,2] & [1989,2,3] \\
003 & 1 & B & Citroen & C2 & [2002,2,2] & [2006,1,1] \\
001 & 2 & B & Peugeot & 206 & [2000,1,2] & [2011,2,1] \\
001 & 3 & B & Peugeot & 207 & [2006,1,1] & [2011,1,1]\\
\hline
\end{tabular}
\vspace{10pt}
\label{tb:car-models}
\vspace{-30pt}
\end{table}

%\subsubsection{The query}
%\paragraph{The query}
Consider the following query:\\
\begin{center}
\emph{The user wants to obtain a list of models from segment B, made by manufacturer Peugeot before the year interval 2001-2005}\\
\end{center}

@@
